TBD

### 2021-03-10 outputs/paper/paper.Rmd
123

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
---

@@

EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Sanders,believed_true)

@@

### post favor by treat
```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Sanders)

ggplot(EDA, aes(x = post_favor_Sanders,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

@@

# deal with missing value
FS<- dat%>%
select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Warren,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake))%>%
na.omit()
## feature selection 
set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, importance=TRUE,proximity=TRUE) ## variable importance

@@

##create model
model <- lm(post_favor_Sanders ~., data =Dummy_data )
summary(model)
```

>>>>

---
title: "TBD"
subtitle: "TBD"
author: "Yingying Zhou, Yang Wu, Xinyi Xu, Hong Pan"
thanks: "Code and data are available at: https://github.com/yangg1224/Political_Deepfake_Videos.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2:
  toc: FALSE
bibliography: references.bib
editor_options: 
  chunk_output_type: console
---

@@

EDA<- dat%>%
        select(treat, response_wave_ID, exp_1_prompt, meta_OS, age_65, educ, PID, crt, gender, age, polknow, internet_usage, ambivalent_sexism, post_favor_Warren,believed_true)

@@

### post favor by treat
```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Warren)

ggplot(EDA, aes(x = post_favor_Warren,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

@@

# deal with missing value
FS<- dat%>%
select(-c(PID_presurvey,comments,PID_leaners,script,quality_pretreat_duration_tooquick,quality_pretreat_duration_tooslow,ambivalent_sexism_1,ambivalent_sexism_2,ambivalent_sexism_3,ambivalent_sexism_4,ambivalent_sexism_5,believed1_true,believed_attackad_true,believed1_attackad_true,believed_offensive,believed_offensive1,believed_funny,believed_funny1,believed_informative,believed_informative1,exp_1_prompt_control,exp_1_prompt_info,exp_2_prompt_control,exp_2_prompt_accuracy,post_favor_Klobuchar,post_favor_Sanders,post_favor_Biden,post_favor_Bloomberg,,exp_2_pct_correct,exp_2_pct_false_fake,exp_2_pct_false_real,post_media_trust1,post_media_trust2,post_media_trust3,post_media_trust,post_dig_lit_1,post_dig_lit_2,post_dig_lit_3,post_dig_lit_4,post_dig_lit_5,post_dig_lit_6,post_dig_lit_7,PID_main,crt1,crt2,crt3,agegroup,treat_control,treat_attackad,treat_fake_text,treat_fake_video,treat_fake_audio,treat_skit,polknow_speaker,polknow_boris,polknow_house,polknow_senate,polknow_veto,polknow_warren,polknow_medicare,quality_demographic_mismatch,quality_failed_backend_attncheck,duration_secs,age,meta_screenres,StartDate,EndDate,meta_resolution,exp_2_hifake,exp_2_lofake,exp_2_nofake))%>%
na.omit()
## feature selection 
set.seed(123)
FS_tree<-randomForest(post_favor_Warren~., data=FS, importance=TRUE,proximity=TRUE) ## variable importance

@@

##create model
model <- lm(post_favor_Warren ~., data =Dummy_data )
summary(model)
```
